### 2013-11-19 article2013.Rmd
Final slides for LCSR conference. Major failure due to outdated browser.
Some basic fixing since Moscow conference. DV table fixed, analysis cleared. Baseline for trying out some more modelling after Moscow discussions.

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% November 2013

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("article2013.Rmd")
system("~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=en -V papersize:a4paper -V documentclass=scrreprt -o article2013.pdf")
# Kuvat kohdalleen - avaa päätte
~/.cabal/bin/pandoc article2013.md --template=../../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=english -V papersize:a4paper -V documentclass=scrreprt -o article2013.tex
sed -i 's/begin{figure}\[htbp\]/begin{figure}\[H\]/g' article2013.tex
xelatex article2013.tex

@@

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5, 
                    caption="Weighted population shares of dependent variable by country",),table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top")

>>>>

% Attributions for Poverty in Post-Socialist Countries[^*]
% Markus Kainu[^**];Mikko Niemelä[^***]
% November 19, 2013

@@

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit("article2013.Rmd")

~/.cabal/bin/pandoc article2013.md --template=../../template/pandoc_article/tex_templates/pandoc.latex.template --number-sections --toc --latex-engine=xelatex -V lang=english -V papersize:a4paper -V documentclass=scrartcl -o article2013.tex
sed -i 's/begin{figure}\[htbp\]/begin{figure}\[H\]/g' article2013.tex
xelatex article2013.tex

@@

--------

@@

```{rattribArticleDescTbl1, results='asis'}
source("code/dv_tables.R")
library(xtable)
print.xtable(xtable(tbl5,digits=1,
                    caption="Weighted population shares of dependent variable by country",),table.placement="H",
             type="latex",
             comment=FALSE, 
             include.rownames=FALSE,
             caption.placement="top",
             size="scriptsize")

### 2013-11-19 descriptive_analysis.Rmd
Some basic fixing since Moscow conference. DV table fixed, analysis cleared. Baseline for trying out some more modelling after Moscow discussions.

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knit("descriptive_analysis.Rmd")
system("pandoc -s descriptive_analysis.md -o descriptive_analysis.html --toc --number-section")

@@

```{rdescplot1_1}
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
library(ggplot2)
library(reshape2)

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions")
library(kaRski)
knit("descriptive_analysis.Rmd")
system("pandoc -s descriptive_analysis.md -o descriptive_analysis.html --toc --number-section")

@@

```{rdescplot1_1}
load("~/workspace/lits/attributions/data/lits.RData")
library(ggplot2)
library(reshape2)

### 2013-11-19 loadClean.Rmd
Now it works. Mikko text included and my corrections with the plots. Now using KOMA script and everything looks good!
Some basic fixing since Moscow conference. DV table fixed, analysis cleared. Baseline for trying out some more modelling after Moscow discussions.

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(kaRski)
knitpandoc("loadClean")
```

@@

summary(factor(lits2$group_analysis))

@@

datQogSum.w$group_general <- factor(datQogSum.w$group_general)

@@

save.image("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
#load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
```

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(kaRski)
knitpandoc("loadClean")
```

@@

lits2$group_analysis <- factor(lits2$group_analysis, levels=c("Western Europe",
                                                             "CEE",
                                                             "CIS",
                                                             NA))

summary(lits2$group_analysis)
```

@@

datQogSum.w$group_general <- factor(datQogSum.w$group_general, 
                                    levels=c("Western Europe",
                                             "CEE",
                                             "CIS"))

@@

save.image("~/workspace/lits/attributions/data/lits.RData")
#load("~/workspace/lits/attributions/data/lits.RData")
```

### 2013-11-19 regressionModelling.Rmd
Some basic fixing since Moscow conference. DV table fixed, analysis cleared. Baseline for trying out some more modelling after Moscow discussions.

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attrib/attrib_year2013/")
library(knitr)
knit("regressionModelling.Rmd")
system("pandoc -s regressionModelling.md -o regressionModelling.html --toc --number-section")

@@

```{rmultilevelLoadData}
#########################################
#########################################
setwd("~/workspace/lits/attrib/attrib_year2013/")

#########################################
load("~/workspace/lits/attrib/attrib_year2013/data/lits.RData")
df.model <- df[df$group_general != "Western Europe",]

>>>>

```{r, eval=FALSE, echo=FALSE}
setwd("~/workspace/lits/attributions/")
library(knitr)
knit("regressionModelling.Rmd")
system("pandoc -s regressionModelling.md -o regressionModelling.html --toc --number-section")

@@

```{rmultilevelLoadData}
#########################################
#########################################
setwd("~/workspace/lits/attributions/")

#########################################
load("~/workspace/lits/attributions/data/lits.RData")
df.model <- df[df$group_general != "Western Europe",]
